---
title: "IPET_analysis"
author: "Bruce"
date: "25 April 2019"
output: html_document
---

Here includes analysis codes for IPET.

**Participants and trial numbers:**
A total of 30 participants are included in this dataset, each participants completed 30 trials thus the total number of trials is 30x30 = 900. 26 trials were deleted due to participants written responses did not conform to the task criteria. Thus, the total number of trials included in the analysis is 874. 

**Data description:**
*Participant:* N=30
*Story_ID:* Story presented to participants on each trial, a total of 30 stories were presented. These stories can be found in IPET_stimuli.xlsx
*Trial:* Trial order presented to participant.
*Condition:* Imagine helping (Experimental:Imagine),Estimate helping (Control:Estimate) and identify journalistic technique (Control:Identify)*
*Gender:* 0-male, 1-female
*Detail.response:* "The imagined media website/scene in your mind was?" (collected for estimate and imagine helping conditions). Responses were made on a 1(simple)-7(detailed) Likert scale. 
*Coherence.response:* "The imagined media website/scene in your mind was?" (collected for estimate and imagine helping conditions). Responses were made on a 1(vague)-7(coherent and clear) Likert scale. 
*Perspective.response:*  "When you identified the media website, imagined helping, or visualized the media website and comments  did you consider  the thoughts and feelings of the person?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (strongly considered). 
*Help.response:* DV of interest. "How likely would you be to help in this situation?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (very willing) Likert scale.
*Trust.response:* DV of interest. "If you are in need of help in the future and the person in the story is nearby, how much do you trust that this person will offer help?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (completely) Likert scale.

*Emotional reaction:*
Emotional reaction (collected for all conditions) rated on a 1(not at all)-7(very strongly) Likert scale for the following emotions:
-	Soft-hearted
-	Troubled 
-	Warm 
-	Distressed
-	Sympathetic
-	Compassionate
-	Disturbed
-	Tender
-	Moved
-	Worried
These measures are included to reduce the possibility of participants correctly guaging the experimental goal and are not utilized in the analyses

#Package and directory set up

```{r setup, include=FALSE}
#Obtain necessary packages
if (!require(pacman)) install.packages('pacman')
#install and load packages
pacman::p_load (sjstats,MuMIn,sjPlot,lme4,lmerTest,lattice,mediation,emmeans,ggeffects,simr,reshape,tidyverse, brms,bayestestR, ggplot2)

#set working directory
setwd('C:/Users/dpen466/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/IPET/IPET/IPET_analysis/IPET_analysis/')

#source custom functions
source("C:/Users/dpen466/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/source/Bayes_scripts.R")
source("C:/Users/dpen466/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/source/LMM_scripts.R")
source('http://faculty.missouri.edu/huangf/data/mcfa/mcfa.R')

# ggplot colours
palette <- c("#eeaa7b", "#00b159", "#00aedb", "#F8766D", "#9590FF", "#CC9933", "#0000FF")
```


##Data setup

```{r}
#Loading data
IPET.df<- read.csv('IPET_fulldata_N=30.csv', header=T)
IPET.df<- IPET.df[complete.cases(IPET.df$Condition),]
IPET.df$Story_ID<- as.factor(IPET.df$Story_ID)
IPET.df$Condition<- as.factor(IPET.df$Condition)
levels (IPET.df$Condition) <- c('Identify', 'Estimate', 'Imagine')
IPET.df$Condition<- relevel(IPET.df$Condition,ref='Identify')

#Centering
IPET.df<- IPET.df%>% 
              mutate(
                #Create dummy variables
                dummy_ident=as.numeric(Condition=='Identify'),
                dummy_img= as.numeric(Condition=='Imagine'),
                dummy_est= as.numeric(Condition=='Estimate'),
                #Create scene imagery measure
                Scene=(Coherence.response+Detail.response)/2,        
                #Within-cluster centering
                Scene_C= group_center(Scene,participant),
                Coherence_C=group_center(Coherence.response,participant),
                Detail_C=group_center(Detail.response,participant),
                Perspective_C =group_center(Perspective.response,participant),
                Help_C=group_center(help.response,participant),
                Trust_C=group_center (trust.response, participant))
#Create data file that only include conceptual helping and imagine condition. This is utilizied for interaction analyses (scene imagery*Condition) and multilevel moderated mediation analysis
interaction.df<- IPET.df%>%
                      filter(Condition!='Identify')%>%
                      mutate(Perspective_C =group_center(Perspective.response,participant),
                             Help_C=group_center(help.response,participant))
interaction.df$Condition<- droplevels(interaction.df$Condition)
```


# Main effect analysis
## Willingenss to help and Trust
### Determine if clustering exist
```{r}
# Help
ranova(lmer(help.response~(1|participant)+(1|Story_ID), data=IPET.df))
#---------------------------------------------------------------------------------------------------------------
# Trust 
ranova(lmer(trust.response~(1|participant)+(1|Story_ID), data=IPET.df))
```
### Main effect models
```{r}
# Parsimonious model -- Help
step(lmer(help.response~Condition+(dummy_est+dummy_img||participant)+(dummy_est+dummy_img||Story_ID), data= IPET.df))
rm_model<- lmer(help.response~Condition+(dummy_est+dummy_img||participant)+(1|Story_ID), data= IPET.df)
fm_help<- lmer(help.response~Condition+(dummy_est+dummy_img|participant)+(1|Story_ID), data= IPET.df)
anova(rm_model,fm_help, refit=F)
# Results
summary(dummy_est+dummy_img)
anova(fm_help, test=' kenward-roger')
(posthoc_help<- emmeans(fm_help,pairwise~Condition,adjust='bonferroni'))
confint(posthoc_help)
r.squaredGLMM(fm_help)
#---------------------------------------------------------------------------------------------------------------
# Parsimonious model -- trust
step(lmer(trust.response~Condition+(dummy_est+dummy_img||participant)+(dummy_est+dummy_img||Story_ID), data= IPET.df))
rm_trust<- lmer(trust.response~Condition+(dummy_img||participant)+(dummy_img||Story_ID), data= IPET.df)
rm_trust<- refit_LMM(rm_trust) #refit 1 time
fm_trust<- lmer(trust.response~Condition+(dummy_img|participant)+(dummy_img|Story_ID), data= IPET.df)
anova(rm_trust,fm_trust,refit=F) #adding in correlation parameter does not include model fit so use 
# Result
summary(rm_trust)
anova(rm_trust, ddf='kenward-roger')
(posthoc_trust<- emmeans(rm_trust,pairwise~Condition,adjust='bonferroni'))
confint(posthoc_trust)
r.squaredGLMM(rm_trust)
```
#### Plots
```{r}
# Help
means_help<- data.frame(posthoc_help$emmeans)
colnames(means_help)[1]<- "Conditions"
bar_plot(means_help) + 
  scale_x_discrete(labels=c("Identify Media Source", "Estimate Helping", "Imagine Helping")) +
  xlab ("Simulation Condition")
# Assess random effect relative to the means random effect
plot_model(fm_help, type= 're')
# Identify as reference group
fm_help2<- lmer(help.response~dummy_est+dummy_img+(dummy_img+dummy_est|participant)+(1|Story_ID), data= IPET.df)
Plot_LMM(fm_help2, 'Identify', 'Estimate', 'Imagine',1)
Plot_LMM(fm_help2, 'Identify', 'Estimate', 'Imagine',2)
Plot_LMM(fm_help2, 'Identify', 'Estimate', 'Imagine',3)
Plot_LMM(fm_help2, 'Identify', 'Estimate', 'Imagine',4)
#Imagine as reference group
fm_help3<- lmer(help.response~dummy_ident+dummy_img+(dummy_img+dummy_ident|participant)+(1|Story_ID), data= IPET.df)
Plot_LMM(fm_help3, 'Estimate', 'Identify', 'Imagine',1)
Plot_LMM(fm_help3, 'Estimate', 'Identify', 'Imagine',2)
Plot_LMM(fm_help3, 'Estimate', 'Identify', 'Imagine',3)
Plot_LMM(fm_help3, 'Estimate', 'Identify', 'Imagine',4)
#---------------------------------------------------------------------------------------------------------------------------------
# Trust
means_trust<- data.frame(posthoc_trust$emmeans)
colnames(means_trust)[1]<- "Conditions"
bar_plot(means_trust) + 
  scale_x_discrete(labels=c("Identify Media Source", "Estimate Helping", "Imagine Helping")) +
  xlab ("Simulation Condition") +
  ylab ("Trust")
#assess random effect relative to the means random effect
plot_model(fm_trust, type= 're')

#Identify as reference group
fm_trust2<- lmer(trust.response~dummy_est+dummy_img+(dummy_img||participant)+(dummy_img||Story_ID), data= IPET.df)
fm_trust2<- refit_LMM(fm_trust2)
Plot_LMM(fm_trust2, 'Identify', 'Estimate', 'Imagine',2)
Plot_LMM(fm_trust2, 'Identify', 'Estimate', 'Imagine',4)
#Imagine as reference group
fm_trust3<- lmer(trust.response~dummy_ident+dummy_img+(dummy_img|participant)+(dummy_img|Story_ID), data= IPET.df)
Plot_LMM(fm_trust3, 'Estimate', 'Identify', 'Imagine',2)
Plot_LMM(fm_trust3, 'Estimate', 'Identify', 'Imagine',4)
```

#### Assumption testing and Power analyses
```{r}
# Help
plot_model (fm_help, type ='diag')

# Trust
plot_model (fm_trust, type ='diag')
#----------------------------------------------------------------------------------------------------------------------------
#Help
pcurve_help <- powerCurve(fm_help, test=fcompare(help.response~1), along='participant')
plot(pcurve_help)

#Trust
pcurve_trust<-powerCurve(rm_trust, test=fcompare(trust.response~1), along='participant')
plot(pcurve_trust)
```


#Interaction analysis: Condition(estimate vs imagine)* Vividness measure
## Willingness to help
```{r}
# Detail 
step(lmer (help.response~Condition*Detail_C+(dummy_img*Detail_C||participant)+(dummy_img*Detail_C||Story_ID),data= interaction.df))
help_rm_det<- lmer (help.response~Condition*Detail_C+(dummy_img+dummy_img:Detail_C||participant)+(1|Story_ID),data= interaction.df)
help_fm_det<- lmer (help.response~Condition*Detail_C+(dummy_img+dummy_img:Detail_C|participant)+(1|Story_ID),data= interaction.df)
help_fm_det<- refit_LMM(help_fm_det)
anova(help_rm_det,help_fm_det,refit=F)

summary(help_fm_det); confint(help_fm_det, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
anova(help_fm_det, ddf='Kenward-Roger')
(posthoc_det_help<- emtrends(help_fm_det,pairwise~Condition,var='Detail_C'))
confint(posthoc_det_help)
r.squaredGLMM(help_fm_det)
#-------------------------------------------------------------------------------------------------------------------------------------
# Coherence
step(lmer (help.response~Condition*Coherence_C+(dummy_img*Coherence_C||participant)+(dummy_img*Coherence_C||Story_ID), data=interaction.df)) 
help_rm_coh<- lmer (help.response~Condition*Coherence_C+(dummy_img||participant)+(Coherence_C||Story_ID),data= interaction.df)
help_fm_coh<- lmer (help.response~Condition*Coherence_C+(dummy_img|participant)+(Coherence_C|Story_ID),data= interaction.df)
anova(help_rm_coh,help_fm_coh,refit=F)

summary(help_fm_coh); confint(help_fm_coh, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
anova(help_fm_coh, ddf='Kenward-Roger')
(posthoc_coh_help<- emtrends(help_fm_coh,pairwise~Condition,var='Coherence_C'))
confint(posthoc_coh_help)
r.squaredGLMM(help_fm_coh)
#-----------------------------------------------------------------------------------------------------------------------------------
# Scene
step(lmer (help.response~Condition*Scene_C+(dummy_img*Scene_C||participant)+(dummy_img*Scene_C||Story_ID),data= interaction.df))
help_rm_scene<- lmer (help.response~Condition*Scene_C+(dummy_img||participant)+(Scene_C||Story_ID),data= interaction.df)
help_rm_scene<- refit_LMM(help_rm_scene)
help_fm_scene<- lmer (help.response~Condition*Scene_C+(dummy_img|participant)+(Scene_C|Story_ID),data= interaction.df)
anova(help_rm_scene,help_fm_scene,refit=F)

summary(help_fm_scene); confint(help_fm_scene, c("ConditionImagine", "Scene_C", "ConditionImagine:Coherence_C"))
anova(help_fm_scene, ddf='Kenward-Roger')
(posthoc_scene_help<- emtrends(help_fm_scene,pairwise~Condition,var='Scene_C'))
confint(posthoc_scene_help)
r.squaredGLMM(help_fm_scene)
```

####Plot the effect
```{r}
#Detail
sd<-sd(interaction.df$Detail_C)
m<-mean(interaction.df$Detail_C)
m-sd;m;m+sd;
ggpredict(help_fm_det, c("Condition","Detail_C [-1.31,0,1.31]"))%>% plot()
ggpredict(help_fm_det, c("Detail_C[-2.62,0,2.62]","Condition"))%>% plot()
#-----------------------------------------------------------------------------------------------------------------------------------------
#Coherence
sd<-sd(interaction.df$Coherence_C)
m<-mean(interaction.df$Coherence_C)
m-sd;m;m+sd;
ggpredict(help_fm_coh, c("Condition","Coherence_C [-1.22,0,1.22]"))%>% plot()
ggpredict(help_fm_coh, c("Coherence_C[-2.44,0,2.44]","Condition"))%>% plot()
```
#### Assumption testing and power analysis
```{r}
# Detail
plot_model (help_fm_det, type ='diag')

# Coherence
plot_model (help_fm_coh, type ='diag')
#------------------------------------------------------------------------------------------------------------------
# Detail
power_det<- lmer (help.response~Condition*Detail_C+(dummy_img|participant)+(1|Story_ID),data= interaction.df)
pcurve_det_help<- powerCurve(power_det, test=fcompare(help.response~Condition), along='participant')
plot(pcurve_det_help)

# Coherence
pcurve_coh_help <- powerCurve(help_fm_coh, test=fcompare(help.response~Condition), along='participant')
plot(pcurve_coh_help)
```


## Trust 

```{r}
# Detail
step(lmer (trust.response~Condition*Detail_C+(dummy_img*Detail_C||participant)+(dummy_img*Detail_C||Story_ID), data=interaction.df))
trust_rm_det<- lmer (trust.response~Condition*Detail_C+(dummy_img+Detail_C||participant)+(dummy_img+dummy_img:Detail_C||Story_ID), data=interaction.df)
trust_rm_det<- refit_LMM(trust_rm_det) # refit twice
trust_fm_det<- lmer (trust.response~Condition*Detail_C+(dummy_img+Detail_C|participant)+(dummy_img+dummy_img:Detail_C|Story_ID), data=interaction.df) # remove intercept and interaction from from story_ID, 0 variance for intercept and multiple refit fail for interaction
trust_fm_det<- lmer (trust.response~Condition*Detail_C+(dummy_img+Detail_C|participant)+(0+dummy_img|Story_ID), data=interaction.df)
trust_fm_det<- refit_LMM(trust_fm_det) # refit one

summary(trust_fm_det); confint(trust_fm_det, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
anova(trust_fm_det, ddf='Kenward-Roger')
(posthoc_det_trust<- emtrends(trust_fm_det,pairwise~Condition,var='Detail_C'))
confint(posthoc_det_trust)
r.squaredGLMM(trust_fm_det)
#-----------------------------------------------------------------------------------------------------------------------------------------
#Coherence
step(lmer (trust.response~Condition*Coherence_C+(dummy_img*Coherence_C||participant)+(dummy_img*Coherence_C||Story_ID), data=interaction.df))
trust_coh_rm<- lmer (trust.response~Condition*Coherence_C+(dummy_img+Coherence_C||participant)+(dummy_img||Story_ID), data=interaction.df)
trust_coh_rm<- refit_LMM(trust_coh_rm) # one refit
trust_fm_coh<- lmer (trust.response~Condition*Coherence_C+(dummy_img+Coherence_C|participant)+(0+dummy_img|Story_ID), data=interaction.df) # remove intercept from story_ID, 0 variance
trust_fm_coh<- refit_LMM(trust_fm_coh)# one refit

summary(trust_fm_coh); confint(trust_fm_coh, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
anova(trust_fm_coh, ddf='Kenward-Roger')
(posthoc_coh_trust<- emtrends(trust_fm_coh,pairwise~Condition,var='Coherence_C'))
confint(posthoc_coh_trust)
r.squaredGLMM(trust_fm_coh)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Scene
step(lmer (trust.response~Condition*Scene_C+(dummy_img*Scene_C||participant)+(dummy_img*Scene_C||Story_ID), data=interaction.df))
trust_scene_rm<- lmer (trust.response~Condition*Scene_C+(dummy_img+Scene_C||participant)+(dummy_img+dummy_img:Scene_C||Story_ID), data=interaction.df) # remove Scene from story ID due to singular fit
trust_fm_scene<-lmer (trust.response~Condition*Scene_C+(dummy_img+Scene_C|participant)+(dummy_img|Story_ID), data=interaction.df) # remove interaction from story due to singular fit
trust_fm_scene<- refit_LMM(trust_fm_scene) # 5 refit

summary(trust_fm_scene); confint(trust_fm_scene, c("ConditionImagine", "Scene_C", "ConditionImagine:Scene_C"))
anova(trust_fm_scene, ddf='Kenward-Roger')
(posthoc_scene_trust<- emtrends(trust_fm_scene,pairwise~Condition,var='Scene_C'))
confint(posthoc_scene_trust)
r.squaredGLMM(trust_fm_scene)
```

####Plot the effect
```{r}
#Detail
sd<-sd(interaction.df$Detail_C)
m<-mean(interaction.df$Detail_C)
m-sd;m;m+sd;
ggpredict(trust_fm_det, c("Condition","Detail_C"))%>% plot()
ggpredict(trust_fm_det, c("Detail_C[-4, 0, 4]","Condition"))%>% plot(limit=c(1,7),show.y.title=F, show.title=F, show.x.title=F, breaks= c(1,2,3,4,5,6,7))
#-----------------------------------------------------------------------------------------------------------------------------------------
#Coherence
sd<-sd(interaction.df$Coherence_C)
m<-mean(interaction.df$Coherence_C)
m-sd;m;m+sd;
ggpredict(trust_fm_coh, c("Condition","Coherence_C [-1.22,0,1.22]"))%>% plot()
ggpredict(trust_fm_coh, c("Coherence_C[-2.44,0,2.44]","Condition"))%>% plot()
ggpredict(trust_fm_scene, c("Scene_C[-4, 0, 4]","Condition"))%>% plot(limit=c(1,7),show.y.title=F, show.title=F, show.x.title=F, breaks= c(1,2,3,4,5,6,7))
```
#### Assumption testing and power analysis
```{r}
#Detail
plot_model(trust_fm_det, type='diag')

#Coherence
plot_model(trust_fm_coh, type='diag')
#---------------------------------------------------------------------------------------------------------------
#Detail
pcurve_det_trust<- powerCurve(trust_fm_det, test=fcompare(trust.response~Condition), along='participant')
plot(pcurve_det_trust)

#Coherence
power_trust<- lmer (trust.response~Condition*Coherence_C+(dummy_img|participant)+(1|Story_ID), data=interaction.df)
pcurve_coh_trust <- powerCurve(power_trust, test=fcompare(trust.response~Condition), along='participant')
plot(pcurve_coh_trust)
```



# MLM Mediation analysis
## Condition -> Perspective -> Help
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Path a
# Identify vs Imagine
step(lmer(Perspective.response~dummy_est +dummy_img+(dummy_est +dummy_img||participant), data= IPET.df))
med.fit_0v2_finalHP<- lmer(Perspective.response~dummy_est +dummy_img+(dummy_img|participant), data= IPET.df)

# Estimate vs Imagine
step(lmer(Perspective.response~dummy_ident +dummy_img+(dummy_ident +dummy_img||participant), data= IPET.df))
med.fit_1v2_FinalHP<- lmer(Perspective.response~dummy_ident +dummy_img+(dummy_ident|participant), data= IPET.df)

# Summaries
summary(med.fit_0v2_finalHP); summary(med.fit_1v2_FinalHP)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Path b and c'
# Identify vs Imagine: 
step(lmer(help.response~dummy_est +dummy_img+Perspective_C+(dummy_est +dummy_img +Perspective_C||participant), data= IPET.df))
out.fit_0v2_finalHP<- lmer(help.response~dummy_est +dummy_img+Perspective_C+(dummy_est+dummy_img|participant), data= IPET.df) # remove Perspective_C convergence failure

# Estimate vs Imagine
step(lmer(help.response~dummy_ident+dummy_img+Perspective_C+(dummy_ident+dummy_img+Perspective_C||participant), data= IPET.df))
out.fit_1v2_finalHP<- lmer(help.response~dummy_ident+dummy_img+Perspective_C+(dummy_ident+dummy_img+Perspective_C|participant), data= IPET.df) # remove Perspective_C convergence failure

# Summaries
summary(out.fit_0v2_finalHP);summary(out.fit_1v2_finalHP)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Mediation Models
# Identify vs Imagine
set.seed(67);med.out_0v2HP <-mediate (med.fit_0v2_finalHP, out.fit_0v2_finalHP, treat='dummy_img', mediator = 'Perspective_C')
summary(med.out_0v2HP);plot(med.out_0v2HP)

# Estimate vs Imagine
set.seed(67);med.out_1v2HP <-mediate (med.fit_1v2_FinalHP, out.fit_1v2_finalHP, treat='dummy_img', mediator='Perspective_C')
summary(med.out_1v2HP);plot(med.out_1v2HP)

# Identify vs Estimate
set.seed(67);med.out_0v1HP <- mediate (med.fit_0v2_finalHP, out.fit_0v2_finalHP, treat='dummy_est', mediator = 'Perspective_C')
summary(med.out_0v1HP)
```


## Condition -> Help -> Trust
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Path a
# Identify vs Imagine
step(lmer(help.response~dummy_est +dummy_img+(dummy_est+dummy_img||participant), data= IPET.df))
med.fit_0v2_finalTH<- lmer(help.response~dummy_est+dummy_img+(dummy_est+dummy_img|participant), data= IPET.df)

# Estimate vs Imagine
step(lmer(help.response~dummy_ident +dummy_img+(dummy_ident +dummy_img||participant), data= IPET.df))
med.fit_1v2_finalTH<- lmer(help.response~dummy_ident+dummy_img+(dummy_img+dummy_ident|participant), data= IPET.df)

# Summary
summary(med.fit_0v2_finalTH);summary(med.fit_1v2_finalTH)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Path b and c'
# Identify vs Imagine
step(lmer(trust.response~dummy_est +dummy_img +Help_C+(dummy_est +dummy_img +Help_C||participant), data= IPET.df))
out.fit_0v2_finalTH<- lmer(trust.response~dummy_est +dummy_img +Help_C+(Help_C|participant), data= IPET.df)

# Estimate vs Imagine
step(lmer(trust.response~dummy_ident+dummy_img+Help_C+(dummy_ident+dummy_img+Help_C||participant), data= IPET.df))
out.fit_1v2_finalTH<- lmer(trust.response~dummy_ident+dummy_img+Help_C+(Help_C|participant), data= IPET.df)

# Summary
summary(out.fit_0v2_finalTH); summary(out.fit_1v2_finalTH)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Identify vs Imagine
set.seed(67);med.out_0v2TH <- mediate (med.fit_0v2_finalTH, out.fit_0v2_finalTH, treat='dummy_img', mediator = 'Help_C')
summary(med.out_0v2TH);plot(med.out_0v2TH)

# Estimate vs Imagine
set.seed(67);med.out_1v2TH <-mediate (med.fit_1v2_finalTH, out.fit_1v2_finalTH, treat='dummy_img', mediator='Help_C')
summary(med.out_1v2TH);plot(med.out_1v2TH)

# Identify vs Estimate
set.seed(67);med.out_0v1TH <- mediate (med.fit_0v2_finalTH, out.fit_0v2_finalTH, treat='dummy_est', mediator = 'Help_C')
summary(med.out_0v1TH)
```


# Multilevel moderated medaition 
## Vividness -> Perspective -> Help
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Detail
interaction.df$imgdet_int<- interaction.df$dummy_img*interaction.df$Detail_C

# Mediation effect across the 2 conditons
med.fit_DP <- lmer (Perspective.response~dummy_img*Detail_C+(imgdet_int|participant),data= interaction.df)
out.fit_DP<- lmer (help.response~dummy_img*Detail_C+Perspective_C+(dummy_img+Perspective_C|participant),data= interaction.df)
set.seed(67);Mod.Med_imgDP <- mediate(med.fit_DP, out.fit_DP,covariates = list(dummy_img = 1), treat="Detail_C", mediator="Perspective_C")
set.seed(67);Mod.Med_estDP <- mediate(med.fit_DP, out.fit_DP, covariates = list(dummy_img = 0), treat="Detail_C", mediator="Perspective_C")

# Moderated mediation analysis
med.fit_DP2 <- lmer (Perspective.response~dummy_img+Detail_C+imgdet_int+(imgdet_int|participant),data= interaction.df) 
out.fit_DP2<- lmer (help.response~dummy_img+Detail_C+Perspective_C+imgdet_int+(dummy_img+Perspective_C|participant),data= interaction.df)
set.seed(67);med.out_DP <- mediate (med.fit_DP2, out.fit_DP2, treat='imgdet_int', mediator = 'Perspective_C')

# Summaries
summary(Mod.Med_estDP);summary(Mod.Med_imgDP);summary(med.out_DP)
summary(med.fit_DP);summary(med.fit_DP2)

# Used to plot a
est_DP<- lmer (Perspective.response~Detail_C+(Detail_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_DP<- lmer (Perspective.response~Detail_C+(Detail_C|participant),data= subset(interaction.df, Condition=='Imagine')) 
summary(est_DP);summary(img_DP)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Coherence
interaction.df$imgcoh_int<- interaction.df$dummy_img*interaction.df$Coherence_C

# Mediation effect across the 2 conditons
med.fit_CP <- lmer (Perspective.response~dummy_img*Coherence_C+(Coherence_C|participant),data= interaction.df) 
out.fit_CP<- lmer (help.response~dummy_img*Coherence_C+Perspective_C+(dummy_img+Perspective_C|participant),data= interaction.df)
set.seed(67);Mod.Med_imgCP <- mediate(med.fit_CP, out.fit_CP,covariates = list(dummy_img = 1), treat="Coherence_C", mediator="Perspective_C")
set.seed(67);Mod.Med_estCP <- mediate(med.fit_CP, out.fit_CP, covariates = list(dummy_img = 0), treat="Coherence_C", mediator="Perspective_C")

# Moderated mediation analysis
med.fit_CP2 <- lmer (Perspective.response~dummy_img+Coherence_C+imgcoh_int+(Coherence_C|participant),data= interaction.df) 
out.fit_CP2<- lmer (help.response~dummy_img+Coherence_C+Perspective_C+imgcoh_int+(dummy_img+Perspective_C|participant),data= interaction.df)
set.seed(67);med.out_CP <- mediate (med.fit_CP2, out.fit_CP2, treat='imgcoh_int', mediator = 'Perspective_C')

# Summaries
summary(Mod.Med_estCP);summary(Mod.Med_imgCP);summary(med.out_CP)
summary(med.fit_DP);summary(out.fit_DP)

#used to plot a
est_CP<- lmer (Perspective.response~Coherence_C+(Coherence_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_CP<- lmer (Perspective.response~Coherence_C+(Coherence_C|participant),data= subset(interaction.df, Condition=='Imagine')) 
summary(est_CP);summary(img_CP)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Scene
interaction.df$imgscene_int<- interaction.df$dummy_img*interaction.df$Scene_C

# Mediation effect across the 2 conditons
med.fit_SP <- lmer (Perspective.response~dummy_img*Scene_C+(imgscene_int|participant),data= interaction.df) 
out.fit_SP<- lmer (help.response~dummy_img*Scene_C+Perspective_C+(dummy_img+Perspective_C|participant),data= interaction.df)
set.seed(67);Mod.Med_imgSP <- mediate(med.fit_SP, out.fit_SP, covariates = list(dummy_img = 1), treat="Scene_C", mediator="Perspective_C")
set.seed(67);Mod.Med_estSP <- mediate(med.fit_SP, out.fit_SP,covariates = list(dummy_img = 0), treat="Scene_C", mediator="Perspective_C")

# Moderated mediation analysis
med.fit_SP2 <- lmer (Perspective.response~dummy_img+Scene_C+imgscene_int+(imgscene_int|participant),data=interaction.df) 
out.fit_SP2<- lmer (help.response~dummy_img+Scene_C+imgscene_int+Perspective_C+(dummy_img+Perspective_C|participant),data= interaction.df) 
set.seed(67);med.out_SP <- mediate (med.fit_SP2, out.fit_SP2, treat='imgscene_int', mediator ='Perspective_C')

# Summaries
summary(Mod.Med_estSP);summary(Mod.Med_imgSP);summary(med.out_SP)
summary(med.fit_SP);summary(out.fit_SP)

# use for plotting SEs
img_SP <- lmer (Perspective.response~dummy_est*Scene_C+(dummy_est+Scene_C|participant),data= interaction.df) 
img_SP<- refit_LMM(img_SP)#refit 4 times
img_HP<- lmer (help.response~dummy_est*Scene_C+Perspective_C+(dummy_est+Perspective_C|participant),data= interaction.df)
summary(img_SP); summary(img_HP)
```



## Vividness -> Help -> Trust
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#-------------------------------------------------------------------------------------------------------------------------------------------
# Detail
med.fit_DH <- lmer (help.response~dummy_img*Detail_C+(dummy_img+imgdet_int|participant),data= interaction.df) 
out.fit_DH<- lmer (trust.response~dummy_img*(Detail_C+Help_C)+(Detail_C+Help_C|participant),data= interaction.df)
set.seed(67);Mod.Med_imgDH <- mediate(med.fit_DH, out.fit_DH,covariates = list(dummy_img = 1), treat="Detail_C", mediator="Help_C")
set.seed(67);Mod.Med_estDH <- mediate(med.fit_DH, out.fit_DH, covariates = list(dummy_img = 0), treat="Detail_C", mediator="Help_C")

# Used to plot a & b
est_DHa<- lmer (help.response~Detail_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_DHa<- lmer (help.response~Detail_C+(Detail_C|participant),data= subset(interaction.df, Condition=='Imagine')) 
est_DHb<- lmer (trust.response~Detail_C+Help_C+(Detail_C+Help_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
est_DHb<- refit_LMM(est_DHb)
img_DHb<- lmer (trust.response~Detail_C+Help_C+(Detail_C+Help_C|participant),data= subset(interaction.df, Condition=='Imagine'))
img_DHb<- refit_LMM(img_DHb)

# Summaries
summary(Mod.Med_estDH);summary(Mod.Med_imgDH)
summary(est_DHa);summary(img_DHa);summary(est_DHb);summary(img_DHb)
#-------------------------------------------------------------------------------------------------------------------------------------------
# Coherence
med.fit_CH <- lmer (help.response~dummy_img*Coherence_C+(dummy_img|participant),data= interaction.df) 
out.fit_CH<- lmer (trust.response~dummy_img*(Coherence_C+Help_C)+(Coherence_C+Help_C|participant),data= interaction.df)
set.seed(67);Mod.Med_imgCH <- mediate(med.fit_CH, out.fit_CH,covariates = list(dummy_img = 1), treat="Coherence_C", mediator="Help_C")
set.seed(67);Mod.Med_estCH <- mediate(med.fit_CH, out.fit_CH, covariates = list(dummy_img = 0), treat="Coherence_C", mediator="Help_C")

# Used to plot a & b
est_CHa<- lmer (help.response~Coherence_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_CHa<- lmer (help.response~Coherence_C+(Coherence_C|participant),data= subset(interaction.df, Condition=='Imagine')) 
est_CHb<- lmer (trust.response~Coherence_C+Help_C+(Coherence_C+Help_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
est_CHb<- refit_LMM(est_CHb)
img_CHb<- lmer (trust.response~Coherence_C+Help_C+(Help_C|participant),data= subset(interaction.df, Condition=='Imagine'))

# Summaries
summary(Mod.Med_estCH);summary(Mod.Med_imgCH)
summary(est_CHa);summary(img_CHa);summary(est_CHb);summary(img_CHb)
#-------------------------------------------------------------------------------------------------------------------------------------------
# Scene
interaction.df$imghelp_int<- interaction.df$dummy_img*interaction.df$Help_C

med.fit_SH <- lmer (help.response~dummy_img*Scene_C+(dummy_img|participant),data= interaction.df) 
out.fit_SH<- lmer (trust.response~dummy_img*(Scene_C+Help_C)+(Scene_C+Help_C+imghelp_int|participant),data= interaction.df)
out.fit_SH<- refit_LMM(out.fit_SH)
set.seed(67);Mod.Med_imgSH <- mediate(med.fit_SH, out.fit_SH,covariates = list(dummy_img = 1), treat="Scene_C", mediator="Help_C")
set.seed(67);Mod.Med_estSH <- mediate(med.fit_SH, out.fit_SH, covariates = list(dummy_img = 0), treat="Scene_C", mediator="Help_C")

# used to plot a & b
est_SHa<- lmer (help.response~Scene_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_SHa<- lmer (help.response~Scene_C+(Scene_C|participant),data= subset(interaction.df, Condition=='Imagine')) 
est_SHb<- lmer (trust.response~Scene_C+Help_C+(Help_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
est_SHb<- refit_LMM(est_SHb)
img_SHb<- lmer (trust.response~Scene_C+Help_C+(Scene_C+Help_C|participant),data= subset(interaction.df, Condition=='Imagine'))
img_SHb<- refit_LMM(img_SHb)

# Summaries
summary(Mod.Med_estSH);summary(Mod.Med_imgSH)
summary(est_SHa);summary(img_SHa);summary(est_SHb);summary(img_SHb)
```
###Plot
```{r}
# Detail and coherence
plot.df<- cbind.data.frame("Vividness"=c("Detail_Imagine", "Coherence_Imagine","Detail_Estimate", "Coherence_Estimate"), 
                           "IE"= c(0.31,0.30,0.02, 0.07),
                           "l_CI"=c(0.20, 0.20, -0.06, -0.01), 
                           "u_CI"=c(0.42, 0.44,0.09, 0.15))
ggplot(plot.df, aes(x=IE, y=Vividness)) +
  geom_point() +
  geom_errorbarh(aes(xmin=l_CI, xmax=u_CI), height=0.5) +
  theme_classic() +
  xlab("Indirect effects") +
  ylab ("Conditions")


# Scene 
plot.df_scene<-cbind.data.frame("Vividness"=c("Scene_Imagine", "Scene_Estimate"), 
                           "IE"= c(0.36,0.05),
                           "l_CI"=c(0.24, -0.02), 
                           "u_CI"=c(0.50, 0.14))
ggplot(plot.df_scene, aes(x=IE, y=Vividness)) +
  geom_point() +
  geom_errorbarh(aes(xmin=l_CI, xmax=u_CI), height=0.5) +
  theme_classic() +
  xlab("Indirect effects") +
  ylab ("Conditions")
```



## Vividness -> Trust -> Help
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#-------------------------------------------------------------------------------------------------------------------------------------------
# Detail
med.fit_DT <- lmer (trust.response~dummy_img*Detail_C+(dummy_img+Detail_C|participant),data= interaction.df) 
out.fit_DT<- lmer (help.response~dummy_img*(Detail_C+Trust_C)+(dummy_img +Trust_C|participant),data= interaction.df)
set.seed(67);Mod.Med_imgDT <- mediate(med.fit_DT, out.fit_DT,covariates = list(dummy_img = 1), treat="Detail_C", mediator="Trust_C")
set.seed(67);Mod.Med_estDT <- mediate(med.fit_DT, out.fit_DT, covariates = list(dummy_img = 0), treat="Detail_C", mediator="Trust_C")

# Used to plot a & b
est_DTa<- lmer (trust.response~Detail_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_DTa<- lmer (trust.response~Detail_C+(Detail_C|participant),data= subset(interaction.df, Condition=='Imagine')) 
est_DTb<- lmer (help.response~Detail_C+Trust_C+(Trust_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_DTb<- lmer (help.response~Detail_C+Trust_C+(Detail_C+Trust_C|participant),data= subset(interaction.df, Condition=='Imagine'))

# Summaries
summary(Mod.Med_estDT);summary(Mod.Med_imgDT)
summary(est_DTa);summary(img_DTa);summary(est_DTb);summary(img_DTb)
#-------------------------------------------------------------------------------------------------------------------------------------------
# Coherence
med.fit_CT <- lmer (trust.response~dummy_img*Coherence_C+(Coherence_C|participant),data= interaction.df) 
out.fit_CT<- lmer (help.response~dummy_img*(Coherence_C+Trust_C)+(dummy_img+Trust_C|participant),data= interaction.df)
out.fit_CT<- refit_LMM(out.fit_CT)
set.seed(67);Mod.Med_imgCT <- mediate(med.fit_CT, out.fit_CT,covariates = list(dummy_img = 1), treat="Coherence_C", mediator="Trust_C")
set.seed(67);Mod.Med_estCT <- mediate(med.fit_CT, out.fit_CT, covariates = list(dummy_img = 0), treat="Coherence_C", mediator="Trust_C")

# Used to plot a & b
est_CTa<- lmer (trust.response~Coherence_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_CTa<- lmer (trust.response~Coherence_C+(1|participant),data= subset(interaction.df, Condition=='Imagine')) 
est_CTb<- lmer (help.response~Coherence_C+Trust_C+(Trust_C|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_CTb<- lmer (help.response~Coherence_C+Trust_C+(1|participant),data= subset(interaction.df, Condition=='Imagine'))

# Summaries
summary(Mod.Med_estCT);summary(Mod.Med_imgCT)
summary(est_CTa);summary(img_CTa);summary(est_CTb);summary(img_CTb)
#-------------------------------------------------------------------------------------------------------------------------------------------
# Scene
med.fit_ST <- lmer (trust.response~dummy_img*Scene_C+(dummy_img+Scene_C|participant),data= interaction.df) 
med.fit_ST<- refit_LMM(med.fit_ST)
out.fit_ST<- lmer (help.response~dummy_img*(Scene_C+Trust_C)+(dummy_img+Trust_C|participant),data= interaction.df)
out.fit_ST<- refit_LMM(out.fit_ST)
set.seed(67);Mod.Med_imgST <- mediate(med.fit_ST, out.fit_ST,covariates = list(dummy_img = 1), treat="Scene_C", mediator="Trust_C")
set.seed(67);Mod.Med_estST <- mediate(med.fit_ST, out.fit_ST, covariates = list(dummy_img = 0), treat="Scene_C", mediator="Trust_C")

# Used to plot a & b
est_STa<- lmer (trust.response~Scene_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_STa<- lmer (trust.response~Scene_C+(1|participant),data= subset(interaction.df, Condition=='Imagine')) 
est_STb<- lmer (help.response~Scene_C+Trust_C+(1|participant),data= subset(interaction.df, Condition=='Estimate')) 
img_STb<- lmer (help.response~Scene_C+Trust_C+(1|participant),data= subset(interaction.df, Condition=='Imagine'))

# Summaries
summary(Mod.Med_estST);summary(Mod.Med_imgST)
summary(est_STa);summary(img_STa);summary(est_STb);summary(img_STb)
```
###Plot
```{r}
# Detail and coherence
plot.df2<- cbind.data.frame("Vividness"=c("Detail_Imagine", "Coherence_Imagine","Detail_Estimate", "Coherence_Estimate"), 
                           "IE"= c(0.10,0.16,0.06, 0.08),
                           "l_CI"=c(0.04, 0.10, -0.04, -0.02), 
                           "u_CI"=c(0.17, 0.25,0.16, 0.18))
ggplot(plot.df2, aes(x=IE, y=Vividness)) +
  geom_point() +
  geom_errorbarh(aes(xmin=l_CI, xmax=u_CI), height=0.5) +
  theme_classic() +
  xlab("Indirect effects") +
  ylab ("Conditions")

# Scene 
plot.df_scene2<-cbind.data.frame("Vividness"=c("Scene_Imagine", "Scene_Estimate"), 
                           "IE"= c(0.15,0.08),
                           "l_CI"=c(0.08, -0.03), 
                           "u_CI"=c(0.23, 0.20))
ggplot(plot.df_scene2, aes(x=IE, y=Vividness)) +
  geom_point() +
  geom_errorbarh(aes(xmin=l_CI, xmax=u_CI), height=0.5) +
  theme_classic() +
  xlab("Indirect effects") +
  ylab ("Conditions")
```
#multilevel factor analysis:emotional reaction using combined dataset
removed intrigued and intent.
Have a 2 factor model with distress and empathy, as well as running a 3factor model of sympathy, distress and concern.
```{r}
emotion_num <- c(18,20,22,24,26,28,30,32,34,36)
emoFA.df<- data.frame ('Participants'=IPET.df$participant, IPET.df[emotion_num])
mcfa_emotreact<- mcfa.input('Participants',emoFA.df)
twofactor <- 'Empathy =~ softhearted.response+warm.response+sympathetic.response+
                        compassionate.response+tender.response+moved.response; 
              Distress=~ troubled.response+distressed.response+disturb.response+worried.response'
threefactor <- 'Concern=~ softhearted.response+warm.response+tender.response+moved.response; 
                Sympathy=~ sympathetic.response+compassionate.response;
                Distress3fact=~ troubled.response+distressed.response+disturb.response+worried.response'
result1_emotreact<- cfa(twofactor, sample.cov=mcfa_emotreact$pw.cov, sample.nobs=mcfa_emotreact$n-mcfa_emotreact$G )
#summary(result1_emotreact,fit.measures=T, standardized=T)
#3 factor is a better model
result2_emotreact<- cfa(twofactor, sample.cov=mcfa_emotreact$pw.cov, sample.nobs=mcfa_emotreact$n-mcfa_emotreact$G )
summary(result2_emotreact,fit.measures=T, standardized=T)

twofactor_loading_emot<-lavPredict(result1_emotreact, newdata=emoFA.df)
threefactor_loading_emot<-lavPredict(result2_emotreact, newdata=emoFA.df)

emotreact.df<- IPET.df

emotreact.df <- cbind(emotreact.df, twofactor_loading_emot,threefactor_loading_emot)
```
mean centering factor loadings
```{r}
emotreact.df$Empathy_C<- group_center(emotreact.df$Empathy, emotreact.df$participant)
emotreact.df$Distress_C <-group_center(emotreact.df$Distress, emotreact.df$participant)

emotreact.df$Empathy_M<- means(emotreact.df$Empathy, emotreact.df$participant)
emotreact.df$Distress_M<- means(emotreact.df$Distress, emotreact.df$participant)

emotreact.df$Empathy_MC<- emotreact.df$Empathy_M-mean(emotreact.df$Empathy_M)
emotreact.df$Distress_MC<- emotreact.df$Distress_M-mean(emotreact.df$Distress_M)

emotreact.df$Empathy_GMC<-emotreact.df$Empathy -mean(emotreact.df$Empathy_M)
```
Empathy 2 fact
below has reference group as ident
```{r}
library(lmerTest)
emotreact.df$Condition<- relevel(emotreact.df$Condition,ref='Identify')

empathy_zcp_2fact<- lmer(help.response~Condition*(Empathy_MC+Empathy_C)+ ((dummy_est+dummy_img)*Empathy_C||participant)+((dummy_est+dummy_img)*(Empathy_C+Empathy_MC)||Story_ID), data= emotreact.df)
empathy_2fact_step<-step(empathy_zcp_2fact)# remove all from story ID , remove dummy_est:EMpathy_C interaction and EMpathy_C from participant

empathy_rm_2fact<- lmer(help.response~Condition*(Empathy_MC+Empathy_C)+(dummy_est+dummy_img+dummy_img:Empathy_C||participant)+(1|Story_ID), data= emotreact.df)

#add correlation 
empathy_final_2fact<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+(dummy_est+dummy_img|participant)+(1|Story_ID), data= emotreact.df)
summary(empathy_opt_2fact)
```
post hoc 
```{r}
emtrends(empathy_final_2fact, pairwise~Condition, var='Empathy_C',adjust='bonferroni')
emmip(empathy_final_2fact, Condition~Empathy_C,cov.reduce = range)
```

distress 2fact 

```{r}
distress_zcp_2fact<- lmer(help.response~Condition*(Distress_C+Distress_MC)+ ((dummy_est+dummy_img)*Distress_C||participant)+((dummy_est+dummy_img)*(Distress_C+Distress_MC)||Story_ID), data= emotreact.df)
distress_2fact_step<- step(distress_zcp_2fact) #remove all in story ID and remove all interactions in participants

distress_rm_2fact<- lmer(help.response~Condition*(Distress_C+Distress_MC)+ (dummy_est+dummy_img+Distress_C||participant)+(1|Story_ID), data= emotreact.df)
#add correlation 
distress_opt_2fact<- lmer(help.response~Condition*(Distress_C+Distress_MC)+ (dummy_est+dummy_img+Distress_C|participant)+(1|Story_ID), data= emotreact.df)
summary(rePCA(distress_opt_2fact));summary(distress_opt_2fact)
distress_final_2fact<- lmer(help.response~Condition*(Distress_C+Distress_MC)+ (dummy_est+dummy_img|participant)+(1|Story_ID), data= emotreact.df)
summary(distress_final_2fact)
```
post hoc 
```{r}
emtrends(distress_final_2fact, pairwise~Condition, var='Distress_C',adjust='bonferroni')
emmip(distress_final_2fact, Condition~Distress_C,cov.reduce = range)
dim(IPET.df)
```




# Bayesian CLMM
## Main effect analysis
### Willingness to help
```{r}
Bayes_help<- brm(data=IPET.df, family=cumulative("logit"),
                      formula= bf(help.response ~ Condition+(Condition|participant)+
                      (Condition|Story_ID)) +
                   lf(disc~ 0+Condition, cmc=F),
                  prior= c(prior(normal (0.2,1), class=b, coef='ConditionImagine'), 
                           prior (normal(0,1), class=b, coef='ConditionEstimate'),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)), 
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T)

# Diagnostic Checks: pp check and traceplots
pp_check(Bayes_help);plot(Bayes_help)
# Rhat and sample sizes
bayes_samples(Bayes_help)

# Summary
summary(Bayes_help, prob=0.89)
# Evidence Ratios (not reported)
(ER_help<-hypothesis(Bayes_help, hypothesis =c("ConditionImagine>0", "ConditionImagine - ConditionEstimate>0", "ConditionEstimate >0"),alpha=0.055, seed=67))
# pd
colMeans(ER_help$samples>0)
# % in ROPE
rope (ER_help$samples, ci=1, range = c(-0.1, 0.1))

# OR
OR_help<- exp(ER_help$samples)
colnames(OR_help)<- c("Imagine-Identify", "Imagine-Estimate", "Estimate-Identify")
posterior_summary(OR_help, probs = c(0.055, 0.945))

# Extract posterior samples 
set.seed(67);posterior_help<- posterior_samples(Bayes_help)
# Latent SD of simulation conditions
latent_SD(posterior_help)
```


#### Plots
```{r}
# Violin plots
PSE_plots_help<- ER_help$samples
colnames(PSE_plots_help)<- c("Identify", "Estimate", "Control_contrast")
PSE_plots_help<- PSE_plots_help %>% gather("Identify", "Estimate","Control_contrast", key= Condition, value= Posterior)
violin_PSE_help<- violin_bayes(PSE_plots_help, HDI_range=c(0.055, 0.945))[[1]]
violin_PSE_help +
  labs(x="Simulation Condition Contrasts", y = "Willingness to help (Logit)")+
  theme(legend.position = "none") +
  scale_x_discrete(labels=c( "Estimate>Identify", 
                             "Imagine>Estimate ", 
                             "Imagine>Identify")) +
  scale_fill_manual(values=c(palette[4], palette[5], palette[3])) +
  scale_color_manual(values = c(palette[4], palette[5], palette[3]))
#-----------------------------------------------------------------------------------------------------------------------
# Predicted probability in each response category
PSE_pplot_help<-conditional_effects(Bayes_help,categorical=T)
plot(PSE_pplot_help)[[1]] +
  scale_x_discrete(labels=c("Identify Media Source", "Estimate Helping", "Imagine Helping")) +
  theme_classic() +
  xlab("Simulation Conditions") +
  ylim (0, 0.45)
```
### Trust
```{r}
Bayes_Trust<- brm(data=IPET.df, family=cumulative("logit"),
                      formula= bf(trust.response ~ Condition + (Condition|participant) +
                      (Condition|Story_ID)) +
                   lf(disc~ 0+Condition, cmc=F),
                  prior= c(prior (normal(0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)), 
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T)

# Diagnostic Checks: pp check and traceplots
pp_check(Bayes_Trust);plot(Bayes_Trust)
# Rhat and sample sizes
bayes_samples(Bayes_Trust)

# Summary
summary(Bayes_Trust, prob=0.89)
# Evidence Ratios (not reported)
(ER_trust<-hypothesis(Bayes_Trust, hypothesis =c("ConditionImagine>0", "ConditionImagine - ConditionEstimate>0", "ConditionEstimate >0"),alpha=0.055, seed=67))
# pd
colMeans(ER_trust$samples>0)
# % in ROPE
rope (ER_trust$samples, ci=1, range = c(-0.1, 0.1))

# OR
OR_trust<- exp(ER_trust$samples)
colnames(OR_trust)<- c("Imagine-Identify", "Imagine-Estimate", "Estimate-Identify")
posterior_summary(OR_trust, probs = c(0.055, 0.945))

# Extract posterior samples 
set.seed(67);posterior_trust<- posterior_samples(Bayes_Trust)
# Latent SD of simulation conditions
latent_SD(posterior_trust)
```


#### Plots
```{r}
# Violin plots
PSE_plots_trust<- ER_trust$samples
colnames(PSE_plots_trust)<- c("Identify", "Estimate", "Control_contrast")
PSE_plots_trust<- PSE_plots_trust %>% gather("Identify", "Estimate","Control_contrast", key= Condition, value= Posterior)
violin_PSE_Trust<- violin_bayes(PSE_plots_trust, HDI_range=c(0.055, 0.945))[[1]]
violin_PSE_Trust  +
  labs(x="Simulation Condition Contrasts", y = "Trust (Logit)")+
  theme(legend.position = "none") +
  scale_x_discrete(labels=c( "Estimate>Identify", 
                             "Imagine>Estimate ", 
                             "Imagine>Identify")) +
  scale_fill_manual(values=c(palette[4], palette[5], palette[3])) +
  scale_color_manual(values = c(palette[4], palette[5], palette[3]))
#-----------------------------------------------------------------------------------------------------------------------
# Predicted probability in each response category
PSE_pplot_trust<-conditional_effects(Bayes_Trust,categorical=T)
plot(PSE_pplot_trust)[[1]] +
  scale_x_discrete(labels=c("Identify Media Source", "Estimate Helping", "Imagine Helping")) +
  theme_classic() +
  xlab("Simulation Conditions") +
  ylim (0, 0.45)
```



